---
title: "My First R Presentation"
author: "Stephanie_Lee_S"
date: "4/18/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Packages and Dataset

In this assignment, I want to show you how I use Plotly to do exploratory data analysis on dataset `economics`, which is already included in the base R.

```{r message=FALSE}
library(plotly)
data("economics")
```

## The First Glance on the Dataset

```{r}
str(economics)
```

## The First Glance on the Dataset

```{r}
summary(economics)
```

## Variables in Dataset `economics`

`economics` dataset is a US economic time series dataset available from <https://fred.stlouisfed.org/>. This dataset is in "wide" format. If you want to look at the "long" format, you should type `data(economics_long)` in your R console.

There are 6 variables in this dataset. I copied the explanation of the variables from the help for `economics`.

- date: Month of data collection
- pce: personal consumption expenditures (billions USD)
- pop: total population (thousands)
- psavert: personal savings rate
- uempmed: median duration of unemployment (weeks)
- unemploy: number of unemployed (thousands)

## Slide with Plot

```{r warning=F}
plot_ly(economics, x = ~date, y = ~pce, color = ~unemploy, 
        mode = 'markers', type = 'scatter')
```

